Verifying Spatial Properties of Array Computations

### 2017-04-15 oopsla17/oopsla17.tex
Add conventions to index scheme & improve

\begin{defn}[Index scheme]
  An $N$-dimensional \emph{index scheme} is a vector of length $N$ of
  extended integer sets, \ie{}, a member of $\mathcal{P}(\bz)^{N}$.
  An equivalent view of these vectors is as an $N$-times finite Cartesian
  product on subsets of $\bz$.  We use $S, T, U$ to denote index
  schemes.

Index schemes can be \emph{projected} in the $i^{\textit{th}}$ dimension by
  $\pi_i : {\mathcal{P}(\bz{})}^N \to \mathcal{P}(\bz{})$ where $1 \leq i
  \leq N$. For an index scheme $I$, we refer to $\pi_i(S)$ as the
  \emph{$i^{th}$ component} of $S$.
\end{defn}

>>>>

\begin{defn}[Index scheme]
  An $N$-dimensional \emph{index scheme} is a vector of length $N$ of
  integer sets, \ie{}, a member of $\mathcal{P}(\bz)^{N}$.
%  An equivalent view of these vectors is as an $N$-times finite Cartesian
%  product on subsets of $\bz$.
  We use $S, T, U$ to denote index schemes. Henceforth, we assume index schemes
  are all $N$-dimensional for some $N$.

  Index schemes can be \emph{projected} in the $i^{\textit{th}}$ dimension by
  $\pi_i : {\mathcal{P}(\bz{})}^N \to \mathcal{P}(\bz{})$. For an index scheme
  $I$, we refer to $\pi_i(S)$ as the \emph{$i^{th}$ component} of $S$. We assume
  that $i$, when used for projection, always lies between $1$ and $N$.
\end{defn}
